Field-informed Reinforcement Learning for Learning Large-Scale Collective Tasks

### 2023-05-15 paper.tex
chore: fix minors
remove first comment on paper levels
chore: add plots for reward and coerage in time
some comments

\usepackage[T1]{fontenc}
\usepackage{amsfonts}
\usepackage{xcolor}
\usepackage{acronym}
\usepackage{amsmath}
\usepackage[ruled]{algorithm2e}
\def\doi#1{\href{https://doi.org/\detokenize{#1}}{\url{https://doi.org/\detokenize{#1}}}}
%
\usepackage{graphicx}

@@

\begin{IEEEkeywords}
aggregate computing, Graph Neural Networks, and Cyber-Physical Swarms.
\end{IEEEkeywords}
%
\ga{Paper levels:
\begin{itemize}
  \item Distributed collective intelligence
  \item GNN and field coordination
  \item Spatial tracking
\end{itemize}
}
\section{Introduction}

@@

In this section, we aim to clarify the components involved in our proposed solution (i.e., architecture), how these components interact with each other to bring the system to perform the collective behaviour (i.e dynamics), and finally, we will detail the learning algorithm designed and used to synthesise the policy (learning algorithm).

@@

Let $\Gamma$ be the aggregate program that takes $G_t$ as input. 

@@

 $o_v = (\theta^v_t, \omega)$.

@@

Since we consider swarm-like systems, that are an example of many-agent systems, 
 the proposed approach follows a \ac{CDTE} learning pattern,

@@

 Finally, to maximise the coverage, 
  we decided to calculate the maximum and minimum distance of the neighbourhood and give more value in case these two values are similar. 
%
This means that the average distance will tend towards the one expressed by the viewing range of each node:
% 
\begin{equation*}
R^{C}_{v} = \frac{d_{max} - d_{min}}{\mathbb{O}}
\end{equation*}
The final reward function is defined as:
\begin{equation*}
R_{v} = \frac{R^a_{v} + R^{\mathcal{N}}_{v} + R^{C}_{v}}{3}
\end{equation*}
Specifically, we decided to express the signal as a \emph{regret}
  as it is a more general measure of the quality of the action taken by the agent.
It is simplify evaluated as:
\begin{equation*}
R^e_{v} = 1 - R_v
\end{equation*}
%

@@

\subsection{Discussion and Results}
\section{Conclusion and Future Work}
\ga{Page budget: 0.5}
\label{sec:conclusion}

>>>>

\usepackage[T1]{fontenc}
\usepackage{amsfonts}
\usepackage{xcolor}
\usepackage{acronym}
\usepackage{amsmath}
\usepackage{subcaption}
\usepackage[ruled]{algorithm2e}
\def\doi#1{\href{https://doi.org/\detokenize{#1}}{\url{https://doi.org/\detokenize{#1}}}}
%
\usepackage{graphicx}

@@

\begin{IEEEkeywords}
aggregate computing, Graph Neural Networks, and Cyber-Physical Swarms.
\end{IEEEkeywords}
%
%\ga{Paper levels:
%\begin{itemize}
%  \item Distributed collective intelligence
%  \item GNN and field coordination
%  \item Spatial tracking
%\end{itemize}
%}
\section{Introduction}

@@

In this section, we discuss the components involved in our proposed solution (i.e., architecture) and how these components interact with each other to bring the system to perform the collective behaviour (i.e dynamics). Finally, we will detail the learning algorithm designed and used to synthesise the policy (i.e., learning algorithm).

@@

Let $\Gamma$ be the aggregate program that takes a graph $G_t$, representing the participating nodes and their neighbourhood relations at time $t$, as input. 

@@

 $o_v = (\theta^v_t, \omega)$. \lukas{we used $o_v$ to describe the observation of node $v$ in section II.C - so this would not include field information, right?}

@@

Since we consider swarm-like systems, which are an example of many-agent systems, 
 the proposed approach follows a \ac{CTDE} learning pattern,

@@

 Finally, to maximise the coverage, 
  we decided to calculate the maximum and minimum distance of the neighbourhood and give more value in case these two values are similar. 
%
This means that the average distance will tend towards the one expressed by the viewing range of each node:
% 
\begin{equation*}
R^{C}_{v} = \frac{d_{max} - d_{min}}{\mathbb{O}}
\end{equation*}
The final reward function is defined as:
\begin{equation*}
R_{v} = \frac{R^a_{v} + R^{\mathcal{N}}_{v} + R^{C}_{v}}{3}
\end{equation*}
Specifically, we decided to express the signal as a \emph{regret}
  as it is a more general measure of the quality of the action taken by the agent.
It is simplify evaluated as:
\begin{equation*}
R^e_{v} = R_v - 1
\end{equation*}
%

@@

\subsection{Discussion and Results}
%% Subfigures of coverage-in-time and reward-in-time

\begin{figure}
  \centering
  \begin{subfigure}[b]{\linewidth}
    \includegraphics[width=\linewidth]{imgs/coverage-in-time}
    \caption{Coverage in time}
    \label{fig:coverage}
  \end{subfigure}
  \begin{subfigure}[b]{\linewidth}
    \includegraphics[width=\linewidth]{imgs/reward-in-time}
    \caption{Reward in time}
    \label{fig:reward}
  \end{subfigure}
  \caption{Coverage and reward in time}
  \label{fig:coverage-reward}
\end{figure}
\section{Conclusion and Future Work}
\ga{Page budget: 0.5}
\label{sec:conclusion}
